### 2018-05-20 response-one.tex

\comment{14}{%
Page 18, line 405: this is implying that fig 10 is similar to fig2! I personally cannot see this in the figures! They look very different. It might be better to regenerate fig 11a but with different color scales that only vary by four choices, then the comparison would be much easier.
}

\response{%
In hindsight, we may have allowed ourselves to be carried away by our own optimism. We have therefore modified our comments in this section to a more self-critical approach about the results. The question is really not whether they look the same or not, but whether they lead to similar---if not equivalent---conclusions. It is our interpretation that they do in the sense that looking at the results obtained with either approach one may walk away with the same conclusion about the simulation as a whole and about how well (or not well) did the simulations turned out with respect to specific areas in the simulation domain. We modified the text to convey this message, now hopefully more clearly than before.
}

\comment{15}{%
Figure 8: I don't know what you mean by y-label ``decision attributes''. Do you mean ``the number of GOF metrics''? why there is no data point for 1 or 11?
}

\response{%
That is right. It should be the number of decision attributes. We modified the figure accordingly. The reason why there is no data for 1 is because the analysis did not yield any tree that would classify the data using a single metric. On the other end, the reason there are no trees with the 11 metrics is because the analysis of the data resulted in the metric C11 not having any participation in the decision process, as shown in Table 6. We also tried other trees for which we removed metrics C5 and C8. In such cases the participations of the metrics changes and so do the topology of the trees. Some of the trees resulting from that analysis did include the metric C11, but with a very small participation, as shown in the new Table 7.
}

@@

\comment{6}{%
Line 61: This sentence should end with a ``?''.
}

\response{%
In our view, these sentences are written as indirect questions and do not require the use of a question mark. To make this clearer, we modified the beginning of the sentences slightly by removing the colon and adding the word ``regarding''.
}

\comment{7}{%
Lines 98--99: It is not clear how the equation for $S$ is applied to values that are a function of period (e.g., the response or Fourier spectrum). Do you follow the guidelines provided by Anderson? If so, what frequency range/bands are you examining?
}

\response{%
Yes, we follow the guidelines of Anderson (2004), but the question of the reviewer gives way to two separate points of those guidelines: first, that in general the equation for $S$ is applied to all values of frequency (or period) for which is computed and then averaged to produce the GOF scores for C8 and C9; and second, that one can do this process for the broadband signals as well as for different frequency bands, and then average the results. The latter of these two points is applicable to not only C8 and C9 but to all metrics. In this study we only use broadband results to avoid the adding other parameters to the validation process such as the width of the frequency bands or the characteristics of the filters. We added a clarification about how the method guidelines were used to address this comment.
}

### 2018-05-20 response-two.tex

% \setlength{\paperwidth}{210mm}
% \setlength{\paperheight}{297mm}% fixed.

\documentclass{article}

\usepackage[review]{myreviewpckg}

\usepackage{textcomp}
\usepackage{simplemargins}
\usepackage{ifpdf}

\ifpdf
	\usepackage[pdftex,bookmarks=false]{hyperref}
\else
	\usepackage{graphics}
	\usepackage{graphicx}
	\usepackage{epsfig}
	\usepackage[dvipdfm,bookmarks=false]{hyperref}
\fi

\hypersetup{
    pdfpagelayout=OneColumn,
	colorlinks = true,
	urlcolor   = blue,
	citecolor  = blue,
	linkcolor  = blue
}

\clubpenalty=10000  % Orphan - First of paragraph left behind
\widowpenalty=10000 % Widow  - Last of paragraph sent ahead

\setallmargins{1in}

\begin{document}

% *****************************************************************
% *********************** Associate Editor ************************
% *****************************************************************

\thispagestyle{empty}
\setcounter{page}{0}

~

\vspace{6em}
\noindent\today

\vspace{5em}
\noindent
Dr.~Thomas Brocher\\
Associate Editor, BSSA\\
BSSA Editorial Office\\
400 Evelyn Ave, Ste 201\\
Albany, CA 94706

\vspace{4em}
\noindent
Dear Dr. Brocher,

\vspace{1em}
\noindent
Thank you again for reviewing our manuscript (BSSA-D-18-00056R1). We are enclosing a response to your comments and suggestions, which we hope you will find satisfactory. To help with the final review, we have assumed all previous changes as accepted, and produced a new annotated manuscript highlighting the latest modifications for your convenience.
\\

\noindent
We look forward to hearing back from you.

\vspace{2em}
\noindent
Sincerely yours,

\vspace{5em}
\noindent
Ricardo Taborda\\
Department of Civil Engineering, and\\
Center for Earthquake Research and Information\\
The University of Memphis

\newpage
\begin{center}
	\bf
	\large
	Authors' Response
\end{center}

\noindent
As done before, below, we provide a response to each comment. The original comments are in italic black font, followed by our responses in regular blue font.
\vspace{2ex}
\newline

\introcomment{~}{%
I appreciate the author's thoughtful response to the reviewers suggestions and to the revisions that they made to their manuscript, which have substantially improved the paper. I think the paper is close to being acceptable for publication, but I have a few minor suggestions for the authors to consider.
}

\response{%
Thank you. We think we have addressed all your suggestions, and hope you will find the new version of our submission acceptable for publication.
}

\comment{1}{%
Figure 2. In the boxes showing the counts of the GOF factors, consider indicating the ranges of Poor, Fair, Good, and Excellent to allow the reader to quickly see that most GOF factors are in the Fair range. Would it also be useful to indicate the average GOF score for each model? This would allow the reader interested in velocity models to more easily which model produced the highest average GOF.
}

\response{%
We modified Figure 2 by including the ranges for poor, fair, good and excellent, as suggested, and modified the figure's caption accordingly. We, however, did not include the average score as it may be misleading to the readers. The reason for that is that the values for the particular case of the 2008 Chino Hills earthquake at high frequencies would suggest that the velocity model CVM-H+GTL is better than CVM-S or CVM-H, but we know that is not generally the case. In a subsequent study (Taborda et al.,~2016), which is cited in the paper, we showed that over a larger collection of events (30), and for the lower frequencies at which the models can be more properly evaluated, the velocity model CVM-S (in its version 4.26.M01) is the one that is most consistent in yielding better simulation results when these are compared to data. We had cited that paper in the Introduction, and recognizing it may be of interest at this point as well, we now modified the end of the first paragraph in the \textbf{Study Dataset} section to reflect that.
}

\comment{2}{%
Line 146. I assume that all 11 of Anderson's metrics were used for the GOFs shown in Figure 2, but this is not explicitly stated. It should be explicitly stated which of Anderson's metrics were used in Figure 2. It may also be worthwhile to comment that the general fit was Fair, and to compare the average GOF score for the 3 velocity models. This information all may be in Taborda and Bielak (2014) but this paper should repeat them so that the readers don't have to look up the older paper.
}

\response{%
That is correct. We now make explicit mention to the fact that those results were obtained using the eleven metrics described earlier and shown in Table 1. Following the explanation in our response to the previous comment, we modified the end of the first paragraph in the \textbf{Study Dataset} section to make reference to the evaluation of the velocity models done later on by Taborda et al.~(2016). We think that, on what regards to comparing velocity models, that reference is better than Taborda and Bielak (2014).
}

\comment{3}{%
Line 165. ``Alright'' is not quite the right word here. I think you mean either acceptable or reasonable. Did you consider other options, such as using only one component for one velocity model? I assume that you wanted as large a dataset as possible, but you should state the reason you followed the approach of using all data.
}

\response{%
Certainly. We fixed the language and added a sentence to explain the reason behind our choice, which was indeed to use a dataset as large as possible. Thank you.
}

\comment{4}{%
Figure 5. Consider adding lines to each plot that would indicate a 1:1 relation between the x and y axes. These lines would highlight datasets that lie on and off this line, as well as help the reader better see the scatter in the data.
}

\response{%
We appreciate this comment. However, we are reluctant to add the 1:1 relationship lines. The reason being that these plots should not be interpreted as typical correlation plots of scattered data are usually interpreted. If we add the line we would be erroneously leading the readers to think these are as any other $x$-$y$ plots correlating showing the relationship of two metrics as seen through the data, and here one also needs to understand that the symbols (or colors) and how well defined are the transitions from one to another are actually equally, and perhaps more important than whether the cloud of data points follow a 1:1 relationship or not. To make this point clearer we added a comment in the text reflecting this point... \textcolor{red}{Adding the comment in the text of the paper is pending on Naeem agreeing with this response}.
}

\comment{5}{%
Line 280. Suggest ``scope of the paper'' rather than ``scope of the study''.
}

\response{%
Done. Thanks for the sugestion.
}

\comment{6}{%
Tables 6 and 7. To make it easier for the reader to easily understand your results, I suggest adding the full title of each metric to the tables from Table 1.
}

\response{%
Thank you for the suggestion. We adopted it and modified Tables 6 and 7 accordingly.
}

\comment{7}{%
Lines 437-443 and 450-456. Throughout the text, but especially in these paragraphs, I suggest making it easier for the reader to understand which metrics matter and which don't. For this reason I would state the full name of the metric, followed by its code. For example, I would write total energy (C4) instead of just C4 or C4 (total energy). The full name of the metric is easily understood by any reader, the code requires the reader to constantly refer to Table 1.
}

\response{%
Thank you for the suggestion. We thought that doing it all throughout the paper would likely be too repetitive and at some points unnecessary. That being said, we completely agree that in these paragraphs of the \textbf{Results} section using the full names would help carry over the main observations we draw from the analysis. We have therefore modified this part of the manuscript in attention to this comment. We also review the format to be consistent, i.e., first the code, then the name within parentheses.
}

\comment{8}{%
Line 479. Suggest ``of the algorithm'' rather than ``from the algorithm''.
}

\response{%
Fixed. Thanks.
}

\comment{9}{%
Lines 497-499. One of the differences between the two results are that the Tree T1 Combination appears to yield a higher percentage of poor and fair scores than the 11-metric score. But I'm not sure because it's actually very hard to compare the counts in Figure 11. A more direct comparison could be made if the counts in the numerical All GOF Scores were combined into Poor, Fair, Good, and Excellent, and plotted over the Tree T1 Combination count in the lower right hand side. These boxes could be shown as dashed or dotted lines and would make this comparison much more quantitative.
}

\response{%
We followed this advise and modified Figure 11 accordingly. We also modified the text in the \textbf{Testing} section.
}

\comment{10}{%
Line 533. Suggest ``to focus'' instead of ``the focus''.
}

\response{%
Done. Thanks.
}

\comment{11}{%
Lastly, it is customary to acknowledge and/or to thank, the journal reviewers for their helpful suggestions.
}

\response{%
Absolutely! We totally forgot about that during the previous revision. Our apologies for that. We have now added our thanks to the reviewers and to you as well.
}

\end{document}

### 2018-05-20 abstract.tex
completed first pass on second review by associate editor

%
It has become common practice to validate ground motion simulations based on a variety of time and frequency metrics scaled to quantify the level of agreement between synthetics and data or other reference solutions. There is, however, no agreement about the importance or weight that it ought to be given to each metric. This leads to their selection often being subjective, either based on intended applications or personal preferences. As a consequence, it is difficult for simulators to identify what modeling improvements are needed, which would be easier if they could \change{focus} on a reduced number of metrics. We present an analysis \change{that looks into eleven} ground motion validation metrics using semi-supervised and supervised machine learning techniques\change{. These techniques} help label and classify goodness-of-fit results with the objective \change{of} prioritizing and narrowing the choice of \change{these metrics. In particular, we use a validation dataset of a series of physics-based ground motion simulations done for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake. We} study the relationships that exist between \change{eleven metrics, and carry out a process where} these metrics are understood as part of a multi-dimensional space. We use a constrained \kmeans{} method, and conduct a subspace clustering analysis to address the implicit high-dimensional effects. This allows us to label the data in our dataset into four validation categories (poor, fair, good, excellent) following \change{previous studies}. We then develop a family of decision trees using the C5.0 algorithm, from which we select a few trees that help narrow the number of metrics leading to a validation prediction into the four referenced categories. These decision trees can be understood as rapid predictors of the quality of a simulation, \change{or as data-informed classifiers} that can help prioritize validation metrics. Our analysis\change{, although limited to the particular dataset used here,} indicates that among the eleven metrics considered, the acceleration response spectra and total energy of velocity are the most dominant ones, followed by the peak ground response in terms of acceleration and velocity.

>>>>

%
It has become common practice to validate ground motion simulations based on a variety of time and frequency metrics scaled to quantify the level of agreement between synthetics and data or other reference solutions. There is, however, no agreement about the importance or weight that it ought to be given to each metric. This leads to their selection often being subjective, either based on intended applications or personal preferences. As a consequence, it is difficult for simulators to identify what modeling improvements are needed, which would be easier if they could focus on a reduced number of metrics. We present an analysis that looks into eleven ground motion validation metrics using semi-supervised and supervised machine learning techniques. These techniques help label and classify goodness-of-fit results with the objective of prioritizing and narrowing the choice of these metrics. In particular, we use a validation dataset of a series of physics-based ground motion simulations done for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake. We study the relationships that exist between eleven metrics, and carry out a process where these metrics are understood as part of a multi-dimensional space. We use a constrained \kmeans{} method, and conduct a subspace clustering analysis to address the implicit high-dimensional effects. This allows us to label the data in our dataset into four validation categories (poor, fair, good, excellent) following previous studies. We then develop a family of decision trees using the C5.0 algorithm, from which we select a few trees that help narrow the number of metrics leading to a validation prediction into the four referenced categories. These decision trees can be understood as rapid predictors of the quality of a simulation, or as data-informed classifiers that can help prioritize validation metrics. Our analysis, although limited to the particular dataset used here, indicates that among the eleven metrics considered, the acceleration response spectra and total energy of velocity are the most dominant ones, followed by the peak ground response in terms of acceleration and velocity.

### 2018-05-20 conclusions.tex
finalized revision, after cleaning
completed first pass on second review by associate editor

We present the \change{results} of a machine learning analysis using semi-supervised and supervised methods on a large dataset comparing synthetics and data based on multiple goodness-of-fit metrics used in ground motion validation with the goal of \change{prioritizing} and \change{reducing} the number of metrics, and develop an application independent decision algorithm. As a result of the data processing analysis, we propose a simplified algorithm based on a decision tree which uses only two metrics as opposed to the initial eleven available in the dataset. In particular, the proposed algorithm uses three (disjunctive decision) steps based on the values obtained for the metrics of the total energy and acceleration response spectra. We also propose rules to allow for the new class-based validation criteria to combine results obtained from different components of motion, and demonstrate that the results obtained with the proposed algorithm using two metrics are comparable to those obtained with the score-based validation results used in other recent validation studies. \change{One} could implement similar rules to combine results from a frequency-band analysis, using, for example, the mode or majority validation class.

We recognize, however, that the proposed decision tree algorithm may not be a definitive one because of a potential bias on the fact that the dataset used here, although large enough from a statistical point of view, came from simulations done for a particular earthquake \myrevision{(one earthquake and three velocity models)} in a particular region. In a future follow-up study it would be ideal to refine the tree adding other simulation datasets (i.e., from different earthquakes, regions, models, \myrevision{metrics,} etcetera) in order to arrive to a sufficiently sound and robust decision tree. The procedural steps laid out here, nonetheless, \change{remain} valid. We showed that the procedure and background information used for clustering and decision making is stable, and it is likely that the metrics of energy and response spectra (along with peak acceleration and velocity as suggested by the additional trees) will prevail as those among the most decisive ones.

This latter point is perhaps the most important conclusion of our study. Identifying the total energy and response spectra metrics as the decisive ones is a key contribution to validation of ground motion simulations. On the one hand, this contributes to clarifying a standing question in the area of validation, and on the other hand, it signals to simulators where the focus should be in the search for improvements in their models.

>>>>

We present the results of a machine learning analysis using semi-supervised and supervised methods on a large dataset comparing synthetics and data based on multiple goodness-of-fit metrics used in ground motion validation with the goal of prioritizing and reducing the number of metrics, and develop an application independent decision algorithm. As a result of the data processing analysis, we propose a simplified algorithm based on a decision tree which uses only two metrics as opposed to the initial eleven available in the dataset. In particular, the proposed algorithm uses three (disjunctive decision) steps based on the values obtained for the metrics of the total energy and acceleration response spectra. We also propose rules to allow for the new class-based validation criteria to combine results obtained from different components of motion, and demonstrate that the results obtained with the proposed algorithm using two metrics are comparable to those obtained with the score-based validation results used in other recent validation studies. One could implement similar rules to combine results from a frequency-band analysis, using, for example, the mode or majority validation class.

We recognize, however, that the proposed decision tree algorithm may not be a definitive one because of a potential bias on the fact that the dataset used here, although large enough from a statistical point of view, came from simulations done for a particular earthquake, in a particular region, and using a particular set of metrics. In a future follow-up study, it would be ideal to refine the tree adding other simulation datasets (i.e., from different earthquakes, regions, models, and using additional metrics) in order to arrive to a sufficiently sound and robust decision tree. The procedural steps laid out here, nonetheless, remain valid, and there is no reason why not to use it also in other contexts utilizing other metrics (e.g., structural responses metrics such as drift ratio) provided that they are properly normalized. In summary, we can say that for the case of the metrics used here, we showed that the procedure and background information used for clustering and decision making is stable, and it is likely that---despite the limitations just described---the metrics of energy and response spectra (along with peak acceleration and velocity as suggested by the additional trees) will prevail as those among the most decisive ones.

Identifying the total energy and response spectra metrics as decisive metrics in the comparisons between synthetics and observations is a key contribution to validation of ground motion simulations. This contributes to clarifying a standing question in the area of validation, and it provides an indication to simulators about where \change{to focus} in the search for improvements in their models.

### 2018-05-20 dataset.tex
completed first pass on second review by associate editor

We select the simulation results and validation analysis done by \citet{Taborda_2014_BSSA} as our \change{\textit{validation dataset}}. In that study, the authors carried out deterministic simulations for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake using a finite-element approach. The simulations, done for a kinematic finite-fault model of the earthquake, were computed for a maximum frequency \fmaxeq{4} and a minimum shear wave velocity \vsmineq{200}. In total, \citet{Taborda_2014_BSSA} did three simulations, each for a different velocity model \citep[CVM-S4, CVM-H, CVM-H+GTL, see][]{Small_2017_SRL}. The modeling domain covered an area of \adomain{180}{135}{km} that included all the major sedimentary basins and other relevant geologic structures in the greater Los Angeles region. Their validation analysis consisted of comparisons with data recorded during the event at 336 ground motion monitoring stations, for the three \change{components} of motion (EW, NS, and UD). The simulation domain and the stations used in that study are shown in Figure \ref{fig:chino-hills}, and a sample of the validation results obtained by the authors using \citeauthor{Anderson_2004_Proc}'s approach is shown in Figure \ref{fig:ref-gof-maps}. This second figure, in particular, shows the spatial distribution of GOF scores (interpolated from the values at each station) for the comparison of the broadband synthetics and data, averaged for all metrics and the three \change{components} of motion.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}

Here, we use the GOF scores obtained by \citet{Taborda_2014_BSSA} independently of the velocity models and/or the \change{components of motion}. \change{We refer to the set of 11 scores associated with a pair of signals as one of the \textit{data samples} that compose our dataset.} Although at times we will make distinctions between the models and the components for visualization purposes, the clustering analysis to be described in the following section was done using \change{all the data samples in the validation dataset}. The motivation behind this choice was that the dataset, as a collection of GOF values, was independent of the simulations and serves here as a generic set of data samples for the purpose of identifying the correlations that exist between the different metrics in Table \ref{tab:metrics}. As such, given the simulations for each velocity model (3), the components of motion (3), and the number of stations used in the validation (336), gave us a large enough \change{dataset, with} 3,024 \change{data samples}. Figure \ref{fig:data-box-plot} illustrates the idea of a lack of dependence on the simulations by comparing the statistical distribution of the GOF scores of the simulations organized by velocity models and components. It is clear that although there are some differences between them, these are negligible. In other words, the statistical distribution of the data for each metric is about the same independently of model or component. Consequently, we felt it was alright to combine all the \change{data samples into a single dataset}.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and \change{components of motion} (NS, EW, UD). In each case, \change{the boxes represent the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), the medians are indicated by a notch in the boxes, and the vertical lines show} the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}

>>>>

We select the simulation results and validation analysis done by \citet{Taborda_2014_BSSA} as our \textit{validation dataset}. In that study, the authors carried out deterministic simulations for the 2008 \eqmag{w} 5.4 Chino Hills, California, earthquake using a finite-element approach. The simulations, done for a kinematic finite-fault model of the earthquake, were computed for a maximum frequency \fmaxeq{4} and a minimum shear wave velocity \vsmineq{200}. In total, \citet{Taborda_2014_BSSA} did three simulations, each for a different velocity model \citep[CVM-S4, CVM-H, CVM-H+GTL, see][]{Small_2017_SRL}. The modeling domain covered an area of \adomain{180}{135}{km} that included all the major sedimentary basins and other relevant geologic structures in the greater Los Angeles region. Their validation analysis consisted of comparisons with data recorded during the event at 336 ground motion monitoring stations, for the three components of motion (EW, NS, and UD). The simulation domain and the stations used in that study are shown in Figure \ref{fig:chino-hills}, and a sample of the validation results obtained by the authors using \citeauthor{Anderson_2004_Proc}'s approach is shown in Figure \ref{fig:ref-gof-maps}. This second figure, in particular, shows the spatial distribution of GOF scores (interpolated from the values at each station) for the comparison of the broadband synthetics and data, \change{for the three velocity models used by \citet{Taborda_2014_BSSA}. In each case, the results are the average of the GOF results for the three components of motion and the scores for the eleven metrics from Table \ref{tab:metrics}. A subsequent study by \citet{Taborda_2016_GJI} using multiple events found that the model CVM-S \citep[version 4.26.M01, see][]{Small_2017_SRL} to be the model that most consistently led to better simulation results. Here, however, we use the GOF scores obtained by \citet{Taborda_2014_BSSA} independently of the velocity models and/or the components of motion}.

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=\textwidth]{figures/pdf/figure-02}
    \caption{Validation results obtained by \citet{Taborda_2014_BSSA} in the form of GOF values across the region of interest obtained from comparisons between simulations for three different velocity models and data recorded at ground motion monitoring stations. \change{The distribution of the results at the bottom show the count of stations on the GOF scale defined by \citet{Anderson_2004_Proc} and the ranges of the validation categories: poor, fair, good and excellent.} The color version of this figure is available only in the electronic edition.}
    \label{fig:ref-gof-maps}
\end{figure*}

We refer to the set of 11 scores associated with a pair of signals \change{from the work done by \citet{Taborda_2014_BSSA}} as one of the \textit{data samples} that compose our dataset. Although at times we will make distinctions between the velocity models and the components of motion for visualization purposes, the clustering analysis to be described in the following section was done using all the data samples in the validation dataset. The motivation behind this choice was that the dataset, as a collection of GOF values, was independent of the simulations and serves here as a generic set of data samples for the purpose of identifying the correlations that exist between the different metrics in Table \ref{tab:metrics}. As such, given the simulations for each velocity model (3), the components of motion (3), and the number of stations used in the validation (336), gave us a large enough dataset, with 3,024 data samples. Figure \ref{fig:data-box-plot} illustrates the idea of a lack of dependence on the simulations by comparing the statistical distribution of the GOF scores of the simulations organized by velocity models and components. It is clear that although there are some differences between them, these are negligible. In other words, the statistical distribution of the data for each metric is about the same independently of model or component. Consequently, \change{and in order to use a dataset as large as possible, we thought it acceptable} to combine all the data samples into a single dataset.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.48\textwidth]{figures/pdf/figure-03}
    \caption{Statistical distribution of the GOF dataset obtained from \citet{Taborda_2014_BSSA} shown in the form of box-plots for each metric (C1 through C11, see Table \ref{tab:metrics}), velocity model (CVM-S, CVM-H, and CVM-H+GTL), and components of motion (NS, EW, UD). In each case, the boxes represent the interquartile range ($\mathrm{IQR} = \mathrm{Q}3 - \mathrm{Q}1$), the medians are indicated by a notch in the boxes, and the vertical lines show the range of the data, with outliers (data less than $\mathrm{Q}1 - 1.5 \mathrm{IQR}$ and greater than $\mathrm{Q}3 + 1.5 \mathrm{IQR}$) shown as scattered dots. The color version of this figure is available only in the electronic edition.}
    \label{fig:data-box-plot}
\end{figure}
